Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-27 papers/thesis-kirstie/thesis.tex
modified abstract

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid. A WCA fluid 
  consists of soft spheres that exhibit the repulsive portion of the 
  Lennard-Jones potential widely used to model the interaction of two 
  neutral atoms. Our cDFT functional is constructed using Soft Fundamental 
  Theory (SFMT) with Tarazona's tensor expression for $\Phi_3$, and Schmidt's
  erf model in which we have incorporated temperature dependent
  parameters to fit the results to those predicted by Monte-Carlo simulations.
  Our functional was successful in predicting the freezing of the WCA fluid 
  with a fairly good match to Monte-Carlo simulations. This result suggests 
  that SFMT may provide a strong foundation for future density functionals 
  that will model real fluids.
}

>>>>

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid, and construct
  pressure-temperature and temperature-density phase diagrams. 
  A WCA fluid consists of soft spheres that exhibit the repulsive 
  portion of the Lennard-Jones potential widely used to model the 
  interaction of two neutral atoms. Our cDFT functional is constructed 
  using Soft Fundamental Theory (SFMT) with Tarazona's tensor expression 
  for $\Phi_3$, and Schmidt's error function model in which we have 
  incorporated our temperature dependent parameters $\alpha$ and $\Xi$. 
  $\Xi$ is found by making the second virial coefficient for the error 
  function potential equal to the second virial coefficient for the WCA 
  potential. Our functional was successful in predicting the freezing of 
  the WCA fluid with a fairly good match to Monte-Carlo simulations. 
  This result suggests that SFMT may provide a strong foundation for 
  future density functionals that will model real fluids.
}
